The problem and promise of scale in multilayer networks

### 2020-01-23 paper/manuscript.Rmd
conclusion
add questions

>>>>

## Conclusions

something something blah blah.

Silk et al. (2018) presented some key multilayer questions in animal behaviour research. While these questions represent an importanting starting point for multilayer networks, we present an additional set of questions relevant to the promise and problem of scale in mutlilayer networks:

  1) How do social phenotypes across scales differently influence fitness? Are some social scales better predictors for different fitness metrics?

  2) Why do individuals associate more strongly with certain conspecifics in some habitats? What, if any, is the role of movement in the context of habitat networks?

  3)
